# Appendix A : Data Catalogue {-}

## Cockburn data catalogue {-}

A summary of the available data categorised by these data types and by agency/supplier is shown below (Table \@ref(tab:A-datacatalogue)). Data is accesible via the `data` folder of the `csiem-data` [GitHub repository](https://github.com/AquaticEcoDynamics/csiem-data). Please refer to the master data catalogue spreadsheet therein for data provenance information.

#### Catalogue

All data entering the sytem is recording in the CSIEM_Data_Catalogue.xlsx spreadsheet found the data-lake directory in the cseim-data github repository.

<br>
```{r datacatalogue, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet <- read_excel('tables/CSIEM_Data_Catalogue_Extract.xlsx', sheet = 1)
theSheet <- theSheet[theSheet$Table == "Data",]
theSheetGroups <- unique(theSheet$Group)
kbl(theSheet[,2:10], caption = "CSIEM Data Catalogue", align = "l",) %>%
  pack_rows(theSheetGroups[1],
            min(which(theSheet$Group == theSheetGroups[1])),
            max(which(theSheet$Group == theSheetGroups[1])),
            background = '#ebebeb') %>%
  pack_rows(theSheetGroups[2],
            min(which(theSheet$Group == theSheetGroups[2])),
            max(which(theSheet$Group == theSheetGroups[2])),
            background = '#ebebeb') %>%
  pack_rows(theSheetGroups[3],
					  min(which(theSheet$Group == theSheetGroups[3])),
					  max(which(theSheet$Group == theSheetGroups[3])),
					  background = '#ebebeb') %>%
row_spec(0, background = "#002B4D", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

<br>

<br>
```{r A-datacatalogue, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet <- read_excel('tables/data_catalogue.xlsx', sheet = 2)
theSheet <- theSheet[theSheet$Table == "Data",]
theSheetGroups <- unique(theSheet$Group)

kbl(theSheet[,4:10], caption = "CSIEM compiled data summary", align = "l",) %>%
pack_rows(theSheetGroups[1],
min(which(theSheet$Group == theSheetGroups[1])),
            max(which(theSheet$Group == theSheetGroups[1])),
background = '#ebebeb') %>%
pack_rows(theSheetGroups[2],
min(which(theSheet$Group == theSheetGroups[2])),
            max(which(theSheet$Group == theSheetGroups[2])),
background = '#ebebeb') %>%
pack_rows(theSheetGroups[3],
min(which(theSheet$Group == theSheetGroups[3])),
					  max(which(theSheet$Group == theSheetGroups[3])),
background = '#ebebeb') %>%
pack_rows(theSheetGroups[4],
min(which(theSheet$Group == theSheetGroups[4])),
          	max(which(theSheet$Group == theSheetGroups[4])),
background = '#ebebeb') %>%
pack_rows(theSheetGroups[5],
min(which(theSheet$Group == theSheetGroups[5])),
            max(which(theSheet$Group == theSheetGroups[5])),
background = '#ebebeb') %>%
pack_rows(theSheetGroups[6],
min(which(theSheet$Group == theSheetGroups[6])),
            max(which(theSheet$Group == theSheetGroups[6])),
background = '#ebebeb') %>%

row_spec(0, background = "#002B4D", bold = TRUE, color = "white") %>%
kable_styling(full_width = F,font_size = 10) %>%
column_spec(2, width_min = "7em") %>%
column_spec(3, width_max = "19em") %>%
column_spec(4, width_min = "10em") %>%
column_spec(5, width_min = "5em") %>%
scroll_box(width = "700px", height = "4600px",
fixed_thead = FALSE)

```

<br>


```
