# (PART)  APPENDICIES {-} 


# A : Data Catalogue {#datacat}


## Cockburn data catalogue {-}

The CSIEM data-set is accessible via the `csiem-data` [GitHub repository](https://github.com/AquaticEcoDynamics/csiem-data). Please refer to the master data catalogue spreadsheet therein for detailed data provenance information. 

A brief summary of the available data categorised by these data types and by agency/supplier is available by viewing the [CSIEM DATA SNAPHOT](https://github.com/SEAF-CS/csiem-data/blob/main/data-governance/csiem_data_snapshot.pdf). Please note, this document is periodically updated, associated with updates to versions to the model and data availability.

For data acecss options please refer to these [ACCESS INSTRUCTIONS](https://github.com/SEAF-CS/csiem-data/wiki/Access).

## Cockburn sensor data summary {-}

A wide diversity of important field observations using advanced sensors have been made over the past two decades within the Cockburn Sound and Owen Anchorage regions. These data-sets provide important information about hydrodynamic and biogeochemical conditions, and are critical to assist in the validation of the model.  The CSIEM data catalogue described above provides a comprehensive picture of all data-sets, however, a specific summary of sensor deployments has been developed and is presented below.

## {.panelset .unnumbered}

### Light related sensors {.unnumbered}
 
```{r A-sensorsummary17light, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet_Names <- list.files(path = "results/DATA/2021_2025/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet_Names2 <- list.files(path = "results/DATA/2013_2024/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet_Names3 <- list.files(path = "results/DATA/2001_2012/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet <- paste(
  "<",'a href="results/DATA/2021_2025/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">",",",
  "<",'a href="results/DATA/2013_2024/HTML/',theSheet_Names2,'"',">",theSheet_Names2,"<",'/a',">",",",
  "<",'a href="results/DATA/2001_2012/HTML/',theSheet_Names3,'"',">",theSheet_Names3,"<",'/a',">",
  sep = "")

theSheet <- str_split_fixed(theSheet, ',', 3)


kbl(theSheet, caption = "Summary of deployed sensors used to measure light within areas around Cockburn Sound and Owen Anchorage.", align = "l",escape = F,col.names = c("V1.6  (2021-2025)","V1.6 (2013-2024)","V1.6 (2001-2012)"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```



### Water quality related sensors {.unnumbered}
 

### Hydrodynamics related sensors {.unnumbered}


## CS-MOORING Profile Explorer {-}

A valuable data source has been the data collected from the eight water quality buoys located within Cockburn Sound that were developed by the WA Department of Water and Environmental Regulation. The installations are described [ON THIS LINK](https://estuaries.dwer.wa.gov.au/cockburn-sound/).

For a period throughout 2021 to 2022, 4 of the water quality buoys supported "profile moorings" where vertical structure in the water column is recorded approximately each hour. As this data-set is more complex than others in the `csiem-data` ecosystem, a separate summary web-page of this data has been prepared to allow exploration of the data. These plots in particular are useful to identify periods throughout the year where particular patterns of temperature, salinity and oxygen exist.


```{block2, hintA2-cs, type='rmdnote2'}

Access the [DWER Mooring Profile Gallery here](./media/csmooring/dwer_mooring_profile_gallery.html).

```


## Ingested data summary plots {-}

Summary images of data within the CSIEM data-warehouse are shown below for different versions.

## {.panelset .unnumbered}

### V1.6 Dataset Overview {.unnumbered}
 
```{r A-datasummary16, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet_Names <- list.files(path = "results/DATA/2021_2025/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet_Names2 <- list.files(path = "results/DATA/2013_2024/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet_Names3 <- list.files(path = "results/DATA/2001_2012/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet <- paste(
  "<",'a href="results/DATA/2021_2025/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">",",",
  "<",'a href="results/DATA/2013_2024/HTML/',theSheet_Names2,'"',">",theSheet_Names2,"<",'/a',">",",",
  "<",'a href="results/DATA/2001_2012/HTML/',theSheet_Names3,'"',">",theSheet_Names3,"<",'/a',">",
  sep = "")

theSheet <- str_split_fixed(theSheet, ',', 3)


kbl(theSheet, caption = "Data summary in CSIEM V1.6 (ingested) data-set. Please note that other data-sets are included in the CSIEM data-lake that may not appear on these images. Please refer to the data snapshot link above for the current data summary list.", align = "l",escape = F,col.names = c("V1.6  (2021-2025)","V1.6 (2013-2024)","V1.6 (2001-2012)"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```



### V1.7 Dataset Overview {.unnumbered}
 
```{r A-datasummary15, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet_Names <- list.files(path = "HTML/Performance/GEN2/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet_Names2 <- list.files(path = "HTML/Performance/TRAN/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet <- paste(
  "<",'a href="HTML/Performance/GEN2/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">",",",
  "<",'a href="HTML/Performance/TRAN/HTML/',theSheet_Names2,'"',">",theSheet_Names2,"<",'/a',">",
  sep = "")

theSheet <- str_split_fixed(theSheet, ',', 2)


kbl(theSheet, caption = "Pending.)", align = "l",escape = F,col.names = c("Pending","Pending"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

