# Appendix B : Results Archive {-}

The aim of this section is to statistically compare the modelling results against historical data collected within Cockbrun Sound and surrounding waters (where available), with outputs of various generations of the CSIEM The model performance in predicting a range of relevant variables including salinity, temperature, nitrogen, phosphorus and total chlorophyll-a, are assessed with a set of statistical metrics.

This appendix is pending and to be updated with the CSIEM modelling progress.

## {.panelset .unnumbered}

### GEN 2 {.unnumbered}

```{r A-testing3, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet <- str_split_fixed(theSheet, ',', 2)


kbl(theSheet, caption = "Model results for GEN 2 nWV nSDG simulation (Generation 2 model without wave or dynamic sediment modules engaged.)", align = "l",escape = F,col.names = c("Generation 2  (TIME SERIES)","Generation 2 (TRANSECT)"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### GEN 1.5 {.unnumbered}

```{r A-testing2, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet <- str_split_fixed(theSheet, ',', 2)


kbl(theSheet, caption = "Model results for Generation 1.5", align = "l",escape = F,col.names = c("Generation 1.5 nALS Data 2017 2022","Generation 1.5 wALS Data 2017 2022"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### GEN 1 {.unnumbered}

```{r A-testing1, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)

kbl(theSheet, caption = "Model results for Generation 1", align = "l",escape = F,col.names = 'Generation 1 2019 2021', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### GEN 0 {.unnumbered}

```{r A-testing, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)

row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### MULTI {.unnumbered}

HCHB _Multiple Model Comparison_

```{r A-testing5, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)

kbl(theSheet, caption = "Comparison of Model Generations 1, 1.5 & 2", align = "l",escape = F,col.names = 'Model Comparison 2017 2022', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### WAVE {.unnumbered}

HCHB _Wave Comparisons_

```{r A-testing6, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)

kbl(theSheet, caption = "Generation 1.5 Wave Analysis", align = "l",escape = F,col.names = 'Generation 1.5', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)

```
