# Appendix B : Results Archive {-}

## Long term assessment of model performance  {-}

The aim of this section is to statistically compare the modelling results against historical data collected within Cockbrun Sound and surrounding waters (where available), with outputs of various generations of the CSIEM The model performance in predicting a range of relevant variables including salinity, temperature, nitrogen, phosphorus and total chlorophyll-a, are assessed with a set of statistical metrics: 

  +	$R$ : regression coefficient; 
  +	$BIAS$ : bias of average prediction to the average observation; 
  +	$RMS$ : root mean square; and 
  +	$NRMS$ : normalized root mean square calculated as $RMS$ normalized by the average of observed values.

The calculations of statistical metrics has been performed for each site where the number of field observations was >10 in the assessment/simulation period. 

The validation plots including the statistics for each site are available via the links in the below table (Table \@ref(tab:A-testing)). The tables are organised based on model generation, in addition to a comparison of the performance of the model generations (termed 'mutli').


## {.panelset .unnumbered}

### GEN 2 {.unnumbered}
 
```{r A-testing3, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet_Names <- list.files(path = "results/Performance/GEN2/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet_Names2 <- list.files(path = "results/Performance/TRAN/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)

theSheet <- paste(
  "<",'a href="results/Performance/GEN2/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">",",",
  "<",'a href="results/Performance/TRAN/HTML/',theSheet_Names2,'"',">",theSheet_Names2,"<",'/a',">",
  sep = "")

theSheet <- str_split_fixed(theSheet, ',', 2)


kbl(theSheet, caption = "Model results for GEN 2 nWV nSDG simulation (Generation 2 model without wave or dynamic sediment modules engaged.)", align = "l",escape = F,col.names = c("Generation 2  (TIME SERIES)","Generation 2 (TRANSECT)"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### GEN 1.5 {.unnumbered}
 

```{r A-testing2, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
library(stringr)

theSheet_Names <- list.files(path = "results/Performance/GEN15/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)


theSheet_Names2 <- list.files(path = "results/Performance/GEN15_ALS/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)


theSheet <- paste(
  "<",'a href="results/Performance/GEN15/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">",",",
  "<",'a href="results/Performance/GEN15_ALS/HTML/',theSheet_Names2,'"',">",theSheet_Names2,"<",'/a',">",
  sep = "")

theSheet <- str_split_fixed(theSheet, ',', 2)


kbl(theSheet, caption = "Model results for Generation 1.5", align = "l",escape = F,col.names = c("Generation 1.5 nALS Data 2017 2022","Generation 1.5 wALS Data 2017 2022"), ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### GEN 1 {.unnumbered}


```{r A-testing1, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet_Names <- list.files(path = "results/Performance/GEN1/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
theSheet <- paste("<",'a href="results/Performance/GEN1/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">", sep = "")
#theSheet <- append(theSheets,'Validation 2019 2021',0)
kbl(theSheet, caption = "Model results for Generation 1", align = "l",escape = F,col.names = 'Generation 1 2019 2021', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```


### GEN 0 {.unnumbered}


```{r A-testing, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet_Names <- list.files(path = "results/Performance/GEN0/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
theSheet <- paste("<",'a href="results/Performance/GEN0/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">", sep = "")
#theSheet <- append(theSheets,'Validation 2013 2016',0)
kbl(theSheet, caption = "Model results for Generation 0", align = "l",escape = F,col.names = 'Generation 0 2013 2019', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```


### MULTI {.unnumbered}
 
HCHB *Multiple Model Comparison*

```{r A-testing5, echo=FALSE, message=FALSE, warning=FALSE}

library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet_Names <- list.files(path = "results/Performance/MULT/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
theSheet <- paste("<",'a href="results/Performance/MULT/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">", sep = "")
#theSheet <- append(theSheets,'Validation 2013 2016',0)

kbl(theSheet, caption = "Comparison of Model Generations 1, 1.5 & 2", align = "l",escape = F,col.names = 'Model Comparison 2017 2022', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)
```

### WAVE {.unnumbered}

HCHB *Wave Comparisons*

```{r A-testing6, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
library(readxl)
library(rmarkdown)
theSheet_Names <- list.files(path = "results/Performance/WAVE/HTML", pattern = NULL, all.files = FALSE,
           full.names = FALSE, recursive = FALSE,
           ignore.case = FALSE, include.dirs = FALSE, no.. = FALSE)
theSheet <- paste("<",'a href="results/Performance/WAVE/HTML/',theSheet_Names,'"',">",theSheet_Names,"<",'/a',">", sep = "")
#theSheet <- append(theSheets,'Validation 2013 2016',0)

kbl(theSheet, caption = "Generation 1.5 Wave Analysis", align = "l",escape = F,col.names = 'Generation 1.5', ) %>%
row_spec(0, background = "#14759e", bold = TRUE, color = "white") %>%
  kable_styling(full_width = T,font_size = 10) %>%
    scroll_box(fixed_thead = FALSE)

```




